Cybersecurity Is Too Important To Be Left To The Specialists

### 2019-01-16 ITiCSE2019.tex
Changes to abstract

\begin{document}
\title{Cybersecurity is too important to be left to the specialists
\\(Abstract 20 January, Paper 27th)}
%\title{What Do We Mean By Cybersecurity?}  Tom's original was this
%\titlenote{}
%\subtitle{Extended Abstract}
%\subtitlenote{}
\author{James H. Davenport}
\orcid{0000-0002-3982-7545}
\affiliation{%
  \institution{University of Bath}
  \streetaddress{}
  \city{Bath} 
  \country{United Kingdom}
}
\email{j.h.davenport@bath.ac.uk}

@@

\def\IntroYear{2014}  % when BCS started asking for CyberSecurity
\begin{abstract}
There are many facets to CyberSecurity education: we address the questions ``what should the generalist computer scientist know'' and ``how well is that being taught''.  (Cyber)Security (if thought about at all) has hisorically been left to specialists, sometimes called ``Information Assurance'', which worked, even if not well, in a waterfall model.  The Agile and DevOps trends have changed devleopment, but not themselves the view of security. Over the last few years, there has been a recogition of the need for change, exemplified by ``DevSecOps''. But if security is not to be left to the experts, then the generalist must know about it.

We consider particularly the UK perspective, where the British Computer Society accredits computing degrees, and (since \IntroYear) insists on a certain CyberSecurity element in all such.
\end{abstract}

>>>>

\begin{document}
\title{Cybersecurity Is Too Important To Be Left To The Specialists}
%\title{What Do We Mean By Cybersecurity Education?}  Tom's original
\author{James H. Davenport}
\orcid{0000-0002-3982-7545}
\affiliation{%
  \institution{University of Bath}
  \streetaddress{}
  \city{Bath} 
  \country{United Kingdom}
}
\email{j.h.davenport@bath.ac.uk}

@@

\def\IntroYear{2014}  % when BCS started asking for CyberSecurity
\begin{abstract}
There are numerous facets to cybersecurity education, from theory to practice, hardware and software, social and technical, to various other dimensions. Whilst various model curricula and associated recommendations exist, in this paper we address the questions ``what should the generalist computer scientist know'' and ``how well is that being taught''.  (Cyber)security -- if thought about at all -- has historically been left to specialists, frequently viewed as a masters level discipline or left to professional practice, sometimes called ``information assurance'', which worked, even if not well, in a waterfall model.  We have seen Agile and DevOps changing software and systems devleopment, but not necessarily the view of security; however, over recent years, there has been a recogition of the need for change, exemplified by the emergence of ``DevSecOps''. If security is not to be left to the experts, then the generalist must know about it. In the context of significant international computer science curriculum reform -- both in compulsory, as well as post-compulsory education -- what does this trend more generally for computer science and informatics education, and how we teach it?

In this paper, we frame a key social and global challenge in computing education by analysing the UK perspective on cybersecurity education, with a substantial national security, economic, and skills policy context, shaping the practical considerations for education professionals from schools through to universities. Through this analysis of policy and practice in the UK, we make a number of recommendations for future cybersecurity educational initiatives, with potential adoption and adaption in other jurisdictions.

% in which a professional body\/learned society accredits university degree programmes, and (since \IntroYear) insists on a certain CyberSecurity element in all such.
\end{abstract}
